Data analysis to support temporary cycleways

### 2020-05-13 README.Rmd
Update readme, include new liverpool map

in the context of increased demand for cycling to keyworker workplaces.

>>>>

in the context of increased demand for cycling to key worker workplaces.

See this [pre-print paper](https://osf.io/7wjb6) for a generalised summary of the methods. This document describes the work in the context of UK planning priorities.
